

\documentclass[11pt,a4paper, sans]{moderncv}        % possible options include font size 
\moderncvstyle{banking}                            % style options are 'casual' 
\moderncvcolor{red}                                % color options 'blue' (default), 
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou 
\usepackage[margin=1in]{geometry}

\name{Haihong}{Shi}

\phone[mobile]{131~2393~2550}                
\email{shh\_name@hotmail.com}                                
\begin{document}

\makecvtitle

\section{Experience}

\cventry{Dec. 2017--Feb. 2018}{Mobile game developer(intership)}{Huanle Entertainment (Shanghai)Technology Co.,Ltd.}{Shanghai}{}{}

\cventry{Nov. 2017}{Captain}{TechCrunch Shanghai Hackathon}{Shanghai}{}{%
\begin{itemize}
\item Challenge A Winner(First Prize)
\item Developed a solution to track the location and stream of people in crowded area based on IoT sniffer which has been adopted by CITIC Industrial Cloud Co. Ltd to improve theis subordinate enterprises.
\end{itemize}}

\cventry{Dec. 2014--Jan. 2017}{Team member}{ACM-ICPC Team of Z.U.F.E.}{Hangzhou}{}{}{% 
\begin{itemize}
\item Learned algorithm \& data structure, solved nearly 800 problems with C/C++.
\item Led \& helped peers from different colleges participating in programming competitions, some of them get prizes in ACM-ICPC Asia Regional and Zhejiang Province Programming Contest.
\item Built \& maintained online judge system of University.
\end{itemize}}


\section{Education}
\cventry{Sep. 2014--present}{B.S.\ in Information and Calculation Science}{Zhejiang University of Finance \& Economics}{Hangzhou}{}{}  % arguments 3 to 6 can be left empty
%\cventry{year--year}{degree}{Institution}{City}{\textit{Grade}}{Description}

\section{Awards}
  \cventry{Dec. 2016}{}{Zhejiang Province Government Scholarship}{Hangzhou}{}{}
  \cventry{Nov. 2016}{Bronze Medal}{ACM International Collegiate Programming Contest, Asia Regional}{Beijing}{}{}
  \cventry{Nov. 2014}{Second Prize}{College Freshmen Debate Competiton}{Hangzhou}{}{}
  
\section{Vocational skills}
  \cvitem{Languages}{C/C++}
  \cvitem{Web front-end}{HTML, CSS, JavaScript}
  \cvitem{Tools}{Vim, Git, \LaTeX}

\section{Languages}
  \cvitemwithcomment{Mandarin}{Native}{}
  \cvitemwithcomment{English}{Fluent}{}

\end{document}


